An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-18 answer-to-reviewers/answer-to-reviewers.tex

We thank the reviewers for their time, consideration and thoughtful comments. Our article has been amended
according to their recommendations. Changes in the text are highlighted in red. In addition, our replies follow.

\section{Reviewer \#1}

\paragraph{This is an interesting contribution to digital processing of images. Alternative approaches to discretization of elastica based on polygonal approximations for discrete elastica and their convergence issues could be mentioned for comparison}

~\\
In section 5, we compare our segmentation model with the work of \cite{schoenemann09linear} which uses a discretization of curvature proposed in \cite{bruckstein96} which $\Gamma$-convergence is proved in \cite{bruckstein01}. We remark that our approach never leaves the digital domain, in other words, it's purely digital and it doesn't rely on any curve representation. The notions of multigrid convergence and $\Gamma$-convergence are not easily comparable. The former is specially designed for digital data, hence more appropriated in our case as our main object is a digital image.
~\\

### 2019-12-18 jmiv.tex
Mispelling

In fact, it is still a very challenging task to efficiently handle
curvature in the context of image segmentation.  State-of-art methods
are in practice difficult to optimize and do not scale easily
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
often unknown. Improving the quality of the curvature estimator has an
important impact on the accuracy of the results, but is
computationally too costly in these methods. \revision{Moreover, parametric approaches to Elastica  as snakes and splines are way to sensitive to the choice of anchor points and  multigrid convergence hasn't been proven for them.}

>>>>

In fact, it is still a very challenging task to efficiently handle
curvature in the context of image segmentation.  State-of-art methods
are in practice difficult to optimize and do not scale easily
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
often unknown. Improving the quality of the curvature estimator has an
important impact on the accuracy of the results, but is
computationally too costly in these methods. \revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}
